---
title       : A multivariable regression example using R
subtitle    : 
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        :  standalone # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

This presents a multivariable regression example using R. We will use the "mtcars" data to analyze the imporant factor that affets the "miles per gallon".

```{r,echo=TRUE}
library(datasets); data(mtcars); require(stats); require(graphics)
summary(lm(mpg~disp+hp+wt,data=mtcars))$coefficients
```

--- .class #id 

## Summary of data
```{r,echo=TRUE}
summary(lm(mpg~disp+hp+wt,data=mtcars))
```

--- .class #id 

## The regression
```{r,echo=TRUE}
pairs(mtcars,panel=panel.smooth,main='mtcars data')
```


--- .class #id 

## Multilevel factor
Except the "miles per gallon", there might exsits some relationship among the left items, we consider a multilevel factor level. We guess that the "drat" and "qsec" might are linear dependent on "disp", "hp", and "wt".
So, we need the 2 levels.

$$Y_1=\beta_{10}+\beta_{11}X_{1}+\beta_{12}X_2+\beta_{13}X_3,$$
$$Y_2=\beta_{20}+\beta_{21}X_{1}+\beta_{22}X_2+\beta_{23}X_3,$$
where 

1. $Y_1$ is "drat", $Y_2$ is "qsec";

2. $X_{1}$ is "disp", $X_{2}$ is "hp", $X_{3}$ is "wt";

3. $\beta_{ij}$ are the coefficients.

